### 2020-09-01 README.Rmd
upd README

S3 `autoplot()` for all implemented spatial resampling methods.

@@

autoplot(resampling, task)
```

@@

```{r spcv-coords-fold}
autoplot(resampling, task, fold_id = 1)
```

@@

```{r spatiotemp, eval=FALSE}
library(plotly)
task_st = tsk("cookfarm")
resampling = rsmp("spcv-cluto", folds = 5)
resampling$instantiate(task_st, time_var = "Date")
autoplot(resampling, task_st, fold_id = 1, point_size = 3)
```

>>>>

S3 `plot()` method for all implemented spatial resampling methods.

@@

plot(resampling, task, crs = 4326)
```

@@

```{r spcv-coords-fold}
plot(resampling, task, fold_id = 1, crs = 4326)
```

@@

```{r spatiotemp, eval=FALSE}
library(plotly)
task_st = tsk("cookfarm")
resampling = rsmp("sptcv-cluto", folds = 5)
resampling$instantiate(task_st, time_var = "Date")
plot(resampling, task_st, fold_id = 1, point_size = 3)
```
